%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Chuanzhu Xu}} & Email : \href{mailto:chuanzhu.xu@gmail.com}{chuanzhu.xu@gmail.com}\\
   & Mobile : +1-267-251-9876 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Temple University}{Philadelphia, PA}
      {Master of Science in Computer Science;  GPA: 3.71}{Aug. 2014 -- Jun. 2016}
    \resumeSubheading
      {University of Science and Technology of China}{Anhui, China}
      {Bachelor of Science in Computer Science and Technology}{Aug. 2011 -- Jun. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PNC Financial Services}{Pittsburgh, PA}
      {Senior Application Developer}{Feb. 2018 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Responsible for leading team of 4 developers to build system automation tools for model execution platform.}
        \resumeItem{}
          {Improved complex financial models performance by implementing the model in python from SAS.}
        \resumeItem{}
          {Designed system architecture and wrote high-level design documents.}
        \resumeItem{}
          {Built Python Slack chatbot interacting Slack API and ServiceNow API for internal incident management. }
      \resumeItemListEnd

    \resumeSubheading
      {PNC Financial Services}{Pittsburgh, PA}
      {Application Developer}{Jun. 2016 - Feb. 2018}
      \resumeItemListStart
        \resumeItem{}
          {Built a new production residential python model with business owner and drive continuous improvement within the modeling process.}
        \resumeItem{}
          {Developed machine learning project to predit probability of default.}  
        \resumeItem{}
          {Prototyped pyspark/hadoop computing engine for CECL credit loss models.}
        \resumeItem{}
          {Built data visualization tool for different macroeconomic data.}
        \resumeItem{}
          {Built Java/Spring Framework backend for web model execution platform.}
        \resumeItem{}
          {Responsible for administration model execution platform by troubleshooting with user and provide system platform support abilities. }    
      \resumeItemListEnd

    \resumeSubheading
      {Christiana Care Health System}{Newark, DE}
      {Software Engineer Intern}{Jan. 2016 - Jun. 2016}
      \resumeItemListStart
        \resumeItem{}
          {Built interactive website to visulize the nationwide flu activity in timeline by using ASP.NET Framework and CDC Infuenza data API.}
    \resumeItemListEnd

      \resumeSubheading
      {Urban Apps and Maps Studio, Temple University}{Philadelphia, PA}
      {Mentor and Software Engineer}{Jun.. 2015 - Jan. 2016}
      \resumeItemListStart
        \resumeItem{}
          {Mentored 10 high school students to develop their coding skills and built a campus security Android app toght together.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Temple University}{Philadelphia, PA}
      {Research and Teaching Assistant}{Jun. 2014 - Jan. 2016}
      \resumeItemListStart
        \resumeItem{Research Assistant - Machine Learning :}
          { Research on machine learning algorithms for time series data. Built an application to help user find street parking spot in New York city.}
        \resumeItem{Teaching Assistant - Mathematical Concepts in Computing:}
          { Involved in creating assignment, exams and conducting recitation sessions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


% %-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{:Python, Java, C\#, Javascript, C/C++ }
     \hfill
     \textbf{Technologies}{: Spark/Hadoop, AWS, Agile/Sprint}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
